---
title: 'Homework 4'
author: "Akash Setti"
date: "2/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```


```{r, echo=TRUE}
df <- read.csv("choco.csv")
head(df)
```

```{r, echo=TRUE}
dim(df)
ggplot(df, aes(x=Review.Date)) + geom_bar()
```
Question set 2:

1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

```{r, echo=TRUE}
ggplot(df, aes(x= Rating)) + geom_histogram()
```
2.Do ratings depend on the cocoa percentage of a chocolate bar?
```{r, echo=TRUE}
df %>%
  ggplot(aes(x = Rating, y = Cocoa.Pct)) +
  geom_point()
```
3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:

```{r, echo=TRUE}
top3 <- dplyr::filter(df, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(top3, aes(x=Company.Location, y= Rating)) + 
  geom_boxplot()
```
4. For a specific company we want to see what year they had the best rating and the worst rating:

```{r, echo=TRUE}
spcompany <- dplyr::filter(df, Company %in% c("A. Morin"))
ggplot(spcompany, aes(x = Review.Date, fill=factor(Rating))) + geom_bar() 
```
